---
title: "Distributions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{distributions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include=FALSE}
devtools::load_all()
library(parallel)
library(pbapply)
library(caret)
library(ggplot2)
library(plotly)
library(dplyr)
library(tidyr)
```
```{r setup}

library(scR)
```

# Simulating VC Dimension

When estimating bounds, we can avoid specifying the dataset, allowing the built-in `gendata` function to automatically benchmark synthetic data with the appropriate dimensionality. The theoretical bounds are distribution-free in the sense that they hold regardless of the probabilities assigned to training examples. This vignette demonstrates the significance of this property through simulation.
```{r}
mylogit <- function(formula, data){
  m <- structure(
    glm(formula=formula,data=data,family=binomial(link="logit")),
    class=c("svrclass","glm")  #IMPORTANT - must use the class svrclass to work correctly
  )
  return(m)
}
mypred <- function(m,newdata){
  out <- predict.glm(m,newdata,type="response")
  out <- factor(ifelse(out>0.5,1,0),levels=c("0","1")) #Important - must specify levels to account for possibility of all observations being classified into the same class in smaller samples
  return(out)
}
```

```{r,warning=FALSE}
br <- scR::br
pvalues <- c(0.5,0.25,0.1,0.01,0.001)
results <- list()
for(i in 1:length(pvalues)){
  results[[i]] <- estimate_accuracy(two_year_recid ~ race + sex + age + juv_fel_count + juv_misd_count + priors_count + charge_degree..misd.fel.,mylogit,maxn=nrow(br),dim=7,predictfn = mypred,method = "Class Imbalance", p = pvalues[i])
}
```

```{r,warning=FALSE}

for(i in 1:length(results)){
  scR::plot_accuracy(results[[i]])
}
```