---
title: "dw-nominate"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{recidivism}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
This
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include=FALSE}
devtools::load_all()
library(parallel)
library(pbapply)
library(caret)
library(ggplot2)
library(plotly)
library(dplyr)
library(tidyr)
```

```{r setup}
library(scR)
```

# Simulating VC Dimension


```{r,warning=FALSE}
library(e1071)
simvcd(model=svm,dim=2,m=100,k=100,maxn=500,packages= list("e1071"))
```


# Replication example: dw-nominate

We use congressional voting data from Lewis et al.  (2022)'s Voteview: Congressional Roll-Call Votes Database to predict ideology score. Below are descriptions of idelogical fiedls 

Ideological Fields:
mid_1: NOMINATE First-dimension midpoint estimate.
mid_2: NOMINATE Second-dimension midpoint estimate.
spread_1: NOMINATE First-dimension spread estimate.
spread_2: NOMINATE Second-dimension spread estimate.
log_likelihood: NOMINATE estimated log-likelihood.


```{r}
votes<- read.csv("CongressionalVotes.csv")
```


```{r}
mysvm <- function(formula, data){
  m <- structure(
    svm(formula=formula,data=data, kernel = "linear"),
    class=c("svrclass","svm")  #IMPORTANT - must use the class svrclass to work correctly
  )
  return(m)
}


mypred <- function(m,newdata){
  out <- predict(m,newdata)
  out <- factor(ifelse(out>0,1,0),levels=c("0","1")) #Important - must specify levels to account for possibility of all observations being classified into the same class in smaller samples
  return(out)
}

vcd <- simvcd(model=mysvm,dim=2,m=100,k=100,maxn=500,predictfn = mypred)
#vcd <- simvcd(model=mysvm,dim=2,m=100,k=100,maxn=500,predictfn = mypred)
```



## Estimating Accuracy Directly

The package also provides utility for users to directly estimate accuracy given assumptions on the data through the `estimate_accuracy` function. Since we already have data collected for this application, we can simply run the function directly on the original dataset:

```{r,warning=FALSE}
results <- estimate_accuracy(nominate_mid_1 ~yea_count+nay_count,svm, votes, predictfn = mypred)
```

The `plot_accuracy` function also provides a useful helper to quickly display the results of the simulation graphically using either the `ggplot2` or `plotly` libraries:

```{r}
fig <- plot_accuracy(results)
fig
```

Or, using `plotly`:

```{r}
fig <- plot_accuracy(results,plottype = "plotly")
fig
```

We can also avoid specifying the dataset, allowing the built-in `gendata` function to automatically benchmark synthetic data with the appropriate dimensionality:

```{r,warning=FALSE}
results <- estimate_accuracy(two_year_recid ~ race + sex + age + juv_fel_count + juv_misd_count + priors_count + charge_degree..misd.fel.,mylogit,maxn=nrow(br),dim=7,predictfn = mypred)
```
Unsurprisingly, the observed accuracy on the synthetic data is much more comparable to that expected based on theoretical bounds, since the target concept is ``learnable'' with the chosen algorithm by construction.

```{r}
fig <- plot_accuracy(results,plottype = "plotly")
fig
```


# Works Cited
Lewis, Jeffrey B., Keith Poole, Howard Rosenthal, Adam Boche, Aaron Rudkin, and Luke Sonnet (2021). Voteview: Congressional Roll-Call Votes Database. https://voteview.com/
