---
title: "ISIS Tweets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{isis_tweets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include=FALSE}
devtools::load_all()
library(parallel)
library(pbapply)
library(caret)
library(ggplot2)
library(plotly)
library(dplyr)
library(tidyr)
library(Matrix)
library(glmnet)
```
```{r setup}

library(scR)
```



# Replication example: Predicting ISIS Tweet Topics

In "From Isolation to Radicalization: Anti-Muslim Hostility and Support for ISIS in the West", Mitts (2018) uses 10-fold cross-validated elastic net to...

```{r}
# From replication package -- setup data
base::load("training_set_en.rdata", .GlobalEnv)
base::load("DTMs_en.rdata", .GlobalEnv)
base::load("response_en.rdata", .GlobalEnv)

as.sparseMatrix <- function(simple_triplet_matrix_sparse) {
  retval <-  sparseMatrix(i=as.numeric(simple_triplet_matrix_sparse$i),
                          j=as.numeric(simple_triplet_matrix_sparse$j),
                          x=as.numeric(as.character(simple_triplet_matrix_sparse$v)),
                          dims=c(simple_triplet_matrix_sparse$nrow, 
                                 simple_triplet_matrix_sparse$ncol),
                          dimnames = dimnames(simple_triplet_matrix_sparse),
                          giveCsparse = TRUE)
}
anti_west_train_x = as.sparseMatrix(dtm_anti_west_en)
```

```{r}
myelnet <- function(formula, data){
  mf <- model.frame(formula,data)
  x <- sparse.model.matrix(formula,mf)
  y <- model.response(mf)
  m <- structure(
    cv.glmnet(x=x, y= y,  family="binomial", type.measure="auc", thresh=1e-2),
    class=c("svrclass","cv.glmnet")  #IMPORTANT - must use the class svrclass to work correctly
  )
  return(m)
}
mypred <- function(m,newdata){
  out <- predict(m,newx=newdata,type="class", s="lambda.1se")
  out <- factor(ifelse(out=="1",1,0),levels=c("0","1")) #Important - must specify levels to account for possibility of all observations being classified into the same class in smaller samples
  return(out)
}
vcd <- simvcd(model=myelnet,dim=dim(anti_west_train_x)[,2],m=100,k=100,maxn=500,predictfn = mypred) #Takes about 20 minutes to run on mid-range test machine (Intel i5-11600K CPU)
```
This then allows us to estimate the minimum sample size $n$ needed to guarantee our chosen accuracy, given an assumed misclassification rate of $0.5$:

```{r}
scb(vcd,epsilon=0.05,delta=0.05,eta=0.05)
```
Note that we can also not specify the VCD and the function will run the simulation automatically, as long as it is provided with the appropriate
```{r,eval=FALSE}
scb(epsilon=0.05,delta=0.05,eta=0.05,theor=F,model=mylogit,dim=7,m=100,k=100,maxn=500,predictfn = mypred)
```
In this case, we know the true VCD dimension (8), so we can also assess the magnitude of the estimation error's impact on the required sample size:

```{r}
abs(scb(vcd,epsilon=0.05,delta=0.05,eta=0.05)-scb(8,epsilon=0.05,delta=0.05,eta=0.05))
```
## Estimating Accuracy Directly

The package also provides utility for users to directly estimate accuracy given assumptions on the data through the `estimate_accuracy` function. Since we already have data collected for this application, we can simply run the function directly on the original dataset:

```{r,warning=FALSE}
br <- scR::br
results <- estimate_accuracy(two_year_recid ~ race + sex + age + juv_fel_count + juv_misd_count + priors_count + charge_degree..misd.fel.,mylogit,br,predictfn = mypred)
```

The `plot_accuracy` function also provides a useful helper to quickly display the results of the simulation graphically using either the `ggplot2` or `plotly` libraries:

```{r}
fig <- plot_accuracy(results)
```

Or, using `plotly`:

```{r}
res2 <- getpac(results,delta = 0.05,epsilon=0.35) 
fig <- plot_accuracy(res2,plottype = "plotly")
fig
```

We can also avoid specifying the dataset, allowing the built-in `gendata` function to automatically benchmark synthetic data with the appropriate dimensionality:

```{r,warning=FALSE}
results <- estimate_accuracy(two_year_recid ~ race + sex + age + juv_fel_count + juv_misd_count + priors_count + charge_degree..misd.fel.,mylogit,maxn=nrow(br),dim=7,predictfn = mypred)
```
Unsurprisingly, the observed accuracy on the synthetic data is much more comparable to that expected based on theoretical bounds, since the target concept is ``learnable'' with the chosen algorithm by construction.

```{r}
res2 <- getpac(results,delta = 0.05,epsilon=0.05) 
fig <- plot_accuracy(res2,plottype = "plotly")
fig
```

If the researcher is interested in estimating the causal effect of the latent concept, the package also supports simultaneous estimation of the effect on statistical power.
```{r,warning=FALSE}
results <- estimate_accuracy(formula=two_year_recid ~ race + sex + age + juv_fel_count + juv_misd_count + priors_count + charge_degree..misd.fel.,
                             model=mylogit,
                             maxn=nrow(br),
                             dim=7,
                             predictfn = mypred,
                             power = T,
                             effect_size=0.5,
                             powersims=1000,
                             alpha=0.05)
```
```{r,warning=FALSE}
polyarchydata <- data %>% select(cont,part,polytrue) %>% unique()
results <- estimate_accuracy(formula=polytrue ~ cont + part,
                             model=mylogit,
                             data = polyarchydata,
                              nsample = 1000,
                             upperlimit = 1000,
                             steps = 20,
                             predictfn = mypred,
                             power = T,
                             effect_size=0.5,
                             powersims=1000,
                             alpha=0.05,
                             parallel = T,
                             coreoffset = 2)
res2 <- getpac(results,delta = 0.01,epsilon=0.05) 
plot_accuracy(res2,plottype="plotly")
```

# Works Cited

Dressel, J. and Farid, H., 2018. The accuracy, fairness, and limits of predicting recidivism. Science advances, 4(1), p.eaao5580.