---
title: "Nonuniform Bounds"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Nonuniform}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include=FALSE}
devtools::load_all()
library(parallel)
library(pbapply)
library(caret)
library(ggplot2)
library(plotly)
library(dplyr)
library(tidyr)
```
```{r setup}

library(scR)
```

# Simulating VC Dimension

When estimating bounds, we can avoid specifying the dataset, allowing the built-in `gendata` function to automatically benchmark synthetic data with the appropriate dimensionality. The theoretical bounds are distribution-free in the sense that they hold regardless of the probabilities assigned to training examples. This vignette demonstrates the significance of this property through simulation.

```{r,warning=FALSE}
results <- estimate_accuracy(two_year_recid ~ race + sex + age + juv_fel_count + juv_misd_count + priors_count + charge_degree..misd.fel.,mylogit,maxn=nrow(br),dim=7,predictfn = mypred)
```